---
title: "255 Demo"
author: '255'
date: "29 August 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,include=TRUE,warning=FALSE}
library(tidyverse)
```
```{r}
#ignore first two columns when reading in data
redditSVData <- read_csv("redditSVuncleanCompound.csv")[ ,c(-1,-2)]
#remove deleted
SV_clean <- redditSVData[!(redditSVData$Reply == "[deleted]"),]
#remove rows that have NA for all
SV_cleanF <- SV_clean[rowSums(is.na(SV_clean)) != ncol(SV_clean),]
str(SV_cleanF)
```
```{r}
#give sentiment values of positive, neutral and negative using typical threshold values used on github
SV_cleanF$sent = "NA"
for (i in 1:nrow(SV_cleanF)){
  if (SV_cleanF[i,]$compound >= 0.05){
    SV_cleanF[i,]$sent <- "Positive"
  } else if (SV_cleanF[i,]$compound <= -0.05){
    SV_cleanF[i,]$sent <- "Negative"
  } else {
    SV_cleanF[i,]$sent <- "Neutral"
  }
}
```
```{r}
names(SV_cleanF)[names(SV_cleanF) == "Key"] <- "Post"
names(SV_cleanF)[names(SV_cleanF) == "sent"] <- "sentiment"
#pie chart of total sentiments
ggplot(SV_cleanF, aes(x="", fill = sentiment)) + geom_bar(width = 1) + coord_polar("y") + scale_fill_manual(values=c("#C70039", "#FFC300", "#2ECC71"))
#bar graph of sentiment in every post
ggplot(SV_cleanF, aes(x=Post, fill = sentiment)) + geom_bar(width = 1) + scale_fill_manual(values=c("#C70039", "#FFC300", "#2ECC71"))
#now without first post (FAQ and beginner questions taken out)
ggplot(SV_cleanF[SV_cleanF$Post != 0, ], aes(x=Post, fill = sentiment)) + geom_bar(width = 1) + scale_fill_manual(values=c("#C70039", "#FFC300", "#2ECC71"))
```
```{r}
sum(SV_cleanF$sentiment == "Positive")
sum(SV_cleanF$sentiment == "Neutral")
sum(SV_cleanF$sentiment == "Negative")
```

```{r}
postPos <- -1
postPosPerc <- 0
postNeu <- -1
postNeuPerc <- 0
postNeg <- -1
postNegPerc <- 0

for (i in 0:499){
    NoPos <- sum((SV_cleanF[SV_cleanF$Post == i, ])$sentiment == "Positive")
    NoNeu <- sum((SV_cleanF[SV_cleanF$Post == i, ])$sentiment == "Neutral")
    NoNeg <- sum((SV_cleanF[SV_cleanF$Post == i, ])$sentiment == "Negative")
    All <- NoPos + NoNeu + NoNeg
    if (All >= 50){
      if (NoPos/All > postPosPerc){
      postPosPerc <- NoPos/All
      postPos <- i
      }
      if (NoNeu/All > postNeuPerc){
        postNeuPerc <- NoNeu/All
        postNeu <- i
      }
      if (NoNeg/All > postNegPerc){
        postNegPerc <- NoNeg/All
        postNeg <- i
      }
    }
}
(postPos) #https://www.reddit.com/r/StardewValley/comments/ipuxa1/hello_fellow_farmers_ive_made_myself_a_cheat/
(postNeu) #https://www.reddit.com/r/StardewValley/comments/irer8u/my_japanese_styled_farm_with_mods/ 
(postNeg) #https://www.reddit.com/r/StardewValley/comments/ipt6ds/well_folks_the_day_has_come_and_i_actually_did/ 

SV_cleanF[which.max(SV_cleanF$compound),]
#0.9987	
#In general, consider watching some YouTube videos of beginner tips and what not to do. There’s a lot out there. That said, here are some of my thoughts: First and foremost, SDV is about having fun. You can min-max but it will spoil the relaxed nature of the game. You may read about a scoring even at the start of year 3, but know that you can continue your farm after that and that you can retro get the scoring event any time after the first one. As such, take the time you want and need. At the start you’re mainly limited by energy; you’ll probably run out energy before you run out of time in the day. Consider what you need to do, usually planting or watering crops, and the rest is for other activities. It is tempting to clear your entire farm of debris etc, but I don’t find that the best investment of time. Clear the area you need, plus a buffer, but there’s no point in clearing the south west if you never go there. Good energy sources are mainly from food. Forageables are often better eaten than sold. In spring you can find spring onions in the forest south of your farm (south eastern corner). From 15 to 18 spring, you can also find salmonberries on the bushes (shown by red berries on the bushes). If you shake the bush, you get the berries. During those days, run around the whole map looking for the berries. They can be a good source of energy for multiple months. There’s an equivalent berry season in fall for blackberries. Running around the map takes **a lot** of time so consider planning where you need to be each day. If you go to the mountains, then the beach, and then the forest, you will spend most of the day running around not doing much. Sundays are the first day of a new week. On that day, forageables reset so consider foraging on Saturday before the reset. Especially at the beach you can find lots of valuable stuff on Saturday. Saves you going there each day. Fridays and Sundays, the traveling merchant comes to the forest. She sells some interesting stuff, but most of that is only really useful if you are looking to min-max. Crops vary in profitability. Some good crops for each season are: strawberries and cauliflower in spring, blueberries in summer, cranberries in fall. You can partially specialise, but other crops can be useful for gifts and community centre bundles. I tend to do 2/3rds cash crops (that I sell) and 1/3rd other crops that I keep in a chest. Keep in mind that the more crops you plant, the more energy you will spend on watering. Watch TV in the morning. It will tell you your luck level and the weather for the next day. If you want to upgrade your watering can, do it (after watering your crop that day) when the next will be rainy. On Sundays, there is a cooking show that can teach you recipes for cooking. The kitchen is unlocked for 10,000g at Robin’s carpenter’s shop. I would wait with unlocking until year 2, but learn the recipes before. On certain days, there will be a show called “Living off the land” which will tell you about what is going on, e.g. berry picking season. Fishing can be a good way to get money. Upgrade to the fibreglass rod to be able to use bait or the iridium rod to use both bait and tackle. The mini game gets easier the more you do it (fishing level makes the green bar bigger). It is a good way to spend some left-over energy. You catch different fish in different areas (mainly: river, lake or ocean). Mining will give you resources you need for crafting. A lot of useful craftables require metals (copper, iron, gold, iridium) which you get from the mines. Give people gifts on their birthdays. The calendar is up at Pierre’s store. Greeting people each day you see them also helps friendship level. You can also give everyone 2 gifts per week (including birthday gift). Once you reach a certain level of friendship with each person, they will sometimes send you gifts by mail. On the wiki you can find what everyone likes, or you can discover it through talking to people or trial and error. Robin can construct buildings for you. This includes a coop and barn for animals (you buy the animals from Marnie). However this is expensive, so you may want to wait a while. Before getting animals, get a silo and cut grass with your scythe to get hay (deposited directly into the silo). One of the buildings is a stable, which gives you the horse. However, this is later game content. A big challenge is doing the Community Centre. It will likely take you into year 2 or beyond to do all tasks there.
SV_cleanF[which.min(SV_cleanF$compound),]
#-0.9864	
#For the first world, the safest strategy is at least for me standing in the corner, because enemies can only attack me from 3 directions instead of 8. For the first boss there's a almost pixel perfect spot where you can shoot at him but he can't shoot at you, basically borderline glitch. Even without it, the boss is really easy so no real tips here. Then If you want to survive in the second world you need at least one damage upgrade (15 coins) because of the fast mushroom enemies that have 2 HP. Basically just try upgrading your damage as much as possible. Then there's the third world.. oh boy. The third world is an absolute hell. There are only 2 enemies but both really strong. Mummies with 8 HP so they take 2 hits even with maxed out damage and imps with I think 4 HP so you can one shot them with upgrades but they're reaaaally fast. Even if you max out your boots I don't think you can outrun them. You just need to be very precise with every single shot, because their spawn rate is almost as fast as them lol. Even one shot missed can result in death here. If you manage to reach Fector - The final boss then I reccomend alt tabing the game and read about his attacks on the wiki because this boss is really tough. If you manage to defeat him then congratulations! You'll get your well deserved achievment and you can now play Prairie King in your own house because you'll get it in the mail box next morning.Well that's about it, sorry if this was kinda messy, English isn't my native language so there's probably a lot of misstakes
SV_cleanF[SV_cleanF$pos == 1,]
SV_cleanF[SV_cleanF$neg == 1,]
```
Negative because talking about beating a game, "beaten" is a negative word but in this context it refers to passing a game. Compound score for "beaten" only is -0.4215. Examples of this in comments is "Have you beaten journey of the prairie king too?", "Dude I can barely beat the first level this is insane to me" and "I have only gotten to the mushroom level. I have beaten the prairie king though". Furthermore, using words that could mean different things in different context such as "You're actually insane" scored -0.4019 although it was a compliment. Funnily enough ":o" scores a negative sentiment score too. 
```{r}
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
```
```{r}
SVreply <- readLines("SVreply.txt")
docs <- Corpus(VectorSource(SVreply))
#inspect(docs)
docs <- tm_map(docs, removeNumbers)
docs <- tm_map(docs, removeWords, stopwords("english"))
#docs <- tm_map(docs, removeWords,c("can", "get", "just"))
#docs <- tm_map(docs, stripWhitespace)
#docs <- tm_map(docs, stemDocument)
```
```{r}
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
head(d, 10)
```
```{r}
set.seed(66553210)
wordcloud(words = d$word, freq = d$freq, min.freq = 100, max.words=150, random.order=FALSE, rot.per=0.30,  colors=brewer.pal(8, "Dark2"))
```
```{r}
ggplot(d[1:10,], mapping = aes(x=word, y=freq)) + geom_col(fill='blue') + scale_x_discrete(limits = d[1:10, 1]) + geom_text(size = 5, vjust = -0.2, label=d[1:10,]$freq) + ggtitle("Most common words in Stardew Valley replies") + theme(plot.title = element_text(hjust = 0.5))
```
```{r}
library(ngram)
#library(stringr)
#library(corpus)
ng <- ngram(SVreply, n=2)
ng.df <- get.phrasetable(ng)
#https://www.rdocumentation.org/packages/qdap/versions/0.2.5/topics/stopwords
#https://cran.r-project.org/web/packages/ngram/vignettes/ngram-guide.pdf
ggplot(ng.df[1:10,], mapping = aes(x=ngrams, y=freq)) + geom_col(fill='blue') + scale_x_discrete(limits = ng.df[1:10, 1], guide = guide_axis(n.dodge = 2)) + geom_text(size = 5, vjust = 1.5, colour = "white", label = ng.df[1:10,]$freq) + ggtitle("Most common bigrams in Stardew Valley replies") + theme(plot.title = element_text(hjust = 0.5)) + labs(x = "bigrams", y = "frequency")
```

```{r}
ng.df2 <- ng.df[c(1, 2, 4, 11, 18, 19, 21, 23 , 25, 37, 39),]
ggplot(ng.df2, mapping = aes(x=ngrams, y=freq)) + geom_col(fill='blue') + scale_x_discrete(limits = ng.df2$ngrams, guide = guide_axis(n.dodge = 2)) + geom_text(size = 5, vjust = 1.5, colour = "white", label = ng.df2$freq) + ggtitle("Most common bigrams related to the game in Stardew Valley replies") + theme(plot.title = element_text(hjust = 0.5)) + labs(x = "bigrams", y = "frequency")
```
```{r}
ng3 <- ngram(SVreply, n=3)
ng3.df <- get.phrasetable(ng3)
ng3.df_clean <- ng3.df[c(3, 4, 5, 6, 7, 9, 11, 16, 17, 18, 19),]
ggplot(ng3.df_clean, mapping = aes(x=ngrams, y=freq)) + geom_col(fill='blue') + scale_x_discrete(limits = ng3.df_clean$ngrams, guide = guide_axis(n.dodge = 3)) + geom_text(size = 5, vjust = 1.5, colour = "white", label = ng3.df_clean$freq) + ggtitle("Most common trigrams related to the game in Stardew Valley replies") + theme(plot.title = element_text(hjust = 0.5)) + labs(x = "trigrams", y = "frequency")
```
```{r}
KaggleAdvanced.df <- read.csv("testDataCompoundAdvanced.csv", header = T)[ ,c(-1,-2)]
kaggleAdvancedF.df <- KaggleAdvanced.df[!(KaggleAdvanced.df$Reply == "deleted"),]
kaggleAdvancedC.df <- kaggleAdvancedF.df[rowSums(is.na(kaggleAdvancedF.df)) != ncol(kaggleAdvancedF.df),]
ggplot(kaggleAdvancedC.df, aes(x="", fill = sentiment)) + geom_bar(width = 1) + coord_polar("y") + scale_fill_manual(values=c("#C70039", "#FFC300", "#2ECC71"))
(sum(kaggleAdvancedC.df$sentiment=="positive"))
(sum(kaggleAdvancedC.df$sentiment=="neutral"))
(sum(kaggleAdvancedC.df$sentiment=="negative"))
```
```{r}
textblob.df <- read.csv("textblob.csv", header = T)[,c(-1,-2,-3)]
textblobClean.df <- textblob.df[!(textblob.df$Reply == "[deleted]"),]
ggplot(textblobClean.df, aes(x="", fill = Classification)) + geom_bar(width = 1) + coord_polar("y") + scale_fill_manual(values=c("#C70039", "#2ECC71"))
sum(textblobClean.df$Classification == "neg")
sum(textblobClean.df$Classification == "pos")
```
```{r}
#textblobClean.df$Reply[194]
```











